NEXTY: A CONSENSUS TO GET ZERO TRANSFER FEE AND INSTANT TRANSFER BLOCKCHAIN

### 2018-08-05 Paper.tex
Update some typos

\pagecolor{pagecolor}
\begin{abstract}
This is the detail technical paper of \href{https://nexty.io}{Nexty Platform}, focusing on describing the operation of a consensus protocol called Proof of Foundation. Proof of Foundation was inspired by the Proof of Authority introduced by \cite{clique} with improvement from \href{https://nexty.io}{Nexty Platform} by introducing a new confirmation system named \textbf{DCCS} - \textbf{D}ual \textbf{C}ryptocurrency \textbf{C}onfirmation \textbf{S}ystem to achieve a absolutely decentralized system and bring a highly incentive system for blockchain maintainers.
\end{abstract}

@@

\section{Block sealing mechanism}\label{sec:sealing}
The {\small DCCS} block sealing mechanism will be implemented  as in following steps. Firstly, the sealers will be numbered from $1$ to $n$ (called ``sealing-id'') randomly at the beginning of each sealing round; in which, $n$ is the number of registered ``authorized-sealer'' and is determined by the state of the smart contract at the \textit{checkpoint block number} of the corresponding sealing round. To ensure the randomness of ``sealing-id'', the numbering is calculated by a hash,  $\boldsymbol{\xi_{\mathrm{k}}}$, as following formula when starting a new sealing round.

@@

After that, the ``sealing-id'' of each authorized-sealer will be taken by the position of \textit{sealing hash}, $\boldsymbol{\xi_k}$, in the array $(\xi_{\mathrm{1}}, \xi_{\mathrm{2}}, ..., \xi_{\mathrm{n}})$, ascending ordered by the \textit{sealing hash}.

>>>>

\pagecolor{pagecolor}
\begin{abstract}
This is the detail technical paper of \href{https://nexty.io}{Nexty Platform}, focusing on describing the operation of a consensus protocol called Proof of Foundation. Proof of Foundation was inspired by the Proof of Authority introduced by \cite{clique} with improvement from \href{https://nexty.io}{Nexty Platform} by introducing a new confirmation system named \textbf{DCCS} - \textbf{D}ual \textbf{C}ryptocurrency \textbf{C}onfirmation \textbf{S}ystem to achieve a decentralized system and bring a highly incentive system for blockchain maintainers.
\end{abstract}

@@

\section{Block sealing mechanism}\label{sec:sealing}
The {\small DCCS} block sealing mechanism will be implemented  as in following steps. Firstly, the sealers will be numbered from $0$ to $n - 1$ (called ``sealing-id'') randomly at the beginning of each sealing round; in which, $n$ is the number of registered ``authorized-sealer'' and is determined by the state of the smart contract at the \textit{checkpoint block number} of the corresponding sealing round. To ensure the randomness of ``sealing-id'', the numbering is calculated by a hash,  $\boldsymbol{\xi_{\mathrm{k}}}$, as following formula when starting a new sealing round.

@@

After that, the ``sealing-id'' of each authorized-sealer will be taken by the position of \textit{sealing hash}, $\boldsymbol{\xi_k}$, in the array $(\xi_{\mathrm{0}}, \xi_{\mathrm{1}}, ..., \xi_{\mathrm{n-1}})$, ascending ordered by the \textit{sealing hash}.
